Soss

### 2020-01-01 paper/paper.tex
pdf
edits

Finally, Soss addresses the well-known challenge of naming things in computer science via Cockney rhyming slang (``sauce pan'' rhymes with ``Stan''). {\bf S}oss is {\bf o}pen-{\bf s}ource {\bf s}oftware.

@@

>>>>

Finally, Soss uses Cockney rhyming slang to address the well-known challenge of naming things in computer science (``sauce pan'' rhymes with ``Stan''). {\bf S}oss is {\bf o}pen-{\bf s}ource {\bf s}oftware.

@@

A Soss model is \emph{function-like}, taking values for its arguments and returning a \emph{joint distribution}.
